Tables

### 2019-11-27 code/tables.rmd
Table 2 error due to sorting RRR10 after RRR1 (corrected)

US_online <- dat %>% #Extract the (max when multiple effects) number of US/online labs per RP
  group_by(rp, effect) %>% 
  summarize(US = sum(country == "USA"),
            online = sum(in_lab == 0, na.rm = TRUE)) %>% 
  group_by(rp) %>% 
  summarize(US = max(US),
            online = max(online)) %>% 
  ungroup() %>% select(US, online)

@@

summary.table <- dat %>% 
  group_by(rp) %>% 
  summarize(Countries = n_distinct(country),
            k = n_distinct(Site), 
            Effects = n_distinct(effect),
            N = if(Effects == 1){sum(Ntotal)}
                           else{sum(Ntotal) / Effects}) %>% #average across effects
  mutate(Paper = papers,
         'Sample and Settings' = sample_settings,
         'Description of Effects' = description,
         'K (US)' = paste0(k, " (", US_online$US, ")")) %>% 
  select(RP = rp, Paper, Countries,'K (US)', everything(), -k) #change order of columns

@@

@@

## Table 3
### Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
```{r prep-heterogeneity-table, cache = TRUE}
#library(metafor)
#library(dplyr)
#library(purrr)

>>>>

US_online <- dat %>% #Extract the (max when multiple effects) number of US/online labs per RP
  group_by(rp, effect) %>% 
  summarize(US = sum(country == "USA"),
            online = sum(in_lab == 0, na.rm = TRUE)) %>% 
  group_by(rp) %>% 
  summarize(US = max(US),
            online = max(online)) %>% 
  ungroup() %>% select(rp, US, online)

@@

summary.table <- dat %>% 
  group_by(rp) %>% 
  summarize(Countries = n_distinct(country),
            k = n_distinct(Site), 
            Effects = n_distinct(effect),
            N = if(Effects == 1){sum(Ntotal)}
                           else{sum(Ntotal) / Effects}) %>% #average across effects
  mutate('K (US)' = paste0(k, " (", US_online$US, ")"))

@@

summary.table <- summary.table %>% 
  mutate(Paper = papers, #In these vectors RRR1-10 are sorted in descending order since they were manually created
         'Sample and Settings' = sample_settings,
         'Description of Effects' = description) %>% 
  select(RP = rp, Paper, Countries,'K (US)', everything(), -k) #change order of columns

@@

## Table 3
### Heterogeneity across primary effects and statistical power of thirteen multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
```{r prep-heterogeneity-table, cache = TRUE}
#library(metafor)
#library(dplyr)
#library(purrr)
